Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-05 paper/manuscript.tex
Add clade specific boxplots to RMSD_heatmap figure

\begin{figure*}
\centering
\includegraphics[width=16cm]{figs/RMSD_heatmap/RMSD_heatmap.pdf}
\caption{\label{fig:RMSD_heatmap}
{\bf Shifts in preferences mapped onto the structure of HA}
(A) The preference shifts as calculated by $RMSD_{corrected}$ between the two HA homologs is mapped onto the structure of HA (PDB 4O5N;~\cite{lee2014receptor}). 
The left structure shows the HA trimer, and the right structure colors one of the monomers. 
The sialic acid receptor is shown in black sticks.
Blue indicates small shifts in preference near zero, while red indicates large shifts in preference.
The top ten most shifted sites are shown in spheres on the monomer.
(B) The stalk domain was found to be significantly less shifted than the head domain (left plot).
Sites absolutely conserved all 18 HA subtypes were also found to be significantly less shifted than the remaining non-conserved sites (right plot).
(C) 
}
\end{figure*}

@@

\begin{suppfigure}
\centerline{\includegraphics[width=\textwidth]{figs/S02_SangerSeq/SangerSeq.pdf}}
\caption{\label{suppfig:SangerSeq}
{\bf Sanger sequencing of 30 clones from the mutant plasmid libraries.} 
(A) 
(B)
(C)
(D)
(E)
}
\end{suppfigure}

>>>>

\begin{figure*}
\centering
\includegraphics[width=17cm]{figs/RMSD_heatmap/RMSD_heatmap.pdf}
\caption{\label{fig:RMSD_heatmap}
{\bf Characterization of the preference shifts}
(A) The preference shifts as calculated by $\textit{RMSD}_\textit{corrected}$ between the two HA homologs is mapped onto the structure of HA (PDB 4O5N;~\cite{lee2014receptor}). 
The left structure shows the HA trimer, and the right structure colors one of the monomers. 
The sialic acid receptor is shown in black sticks.
Blue indicates small shifts in preference near zero, while red indicates large shifts in preference.
(B) The stalk domain was found to be significantly less shifted than the head domain (left plot).
Sites absolutely conserved all 18 HA subtypes were also found to be significantly less shifted than the remaining non-conserved sites (middle plot).
Sites specific to the clade containing H1, H2, H5, and H6 and specific to the H3, H4, and H14 clade are significantly more shifted than non-clade-specific sites (right plot).
(C) HA group-specific interactions between sites 107 and 75(HA2) play a role in determining the upward translation of the globular head domain relative to the stalk domain.
The amino acids at sites 107 and 75(HA2) are shown in spheres on the structure of H1 and H3. 
One monomer is shown in dark gray, while the HA1 domain of the neighboring monomer is in lighter gray.
The sphere colors correspond to the shift in preference at that site.
The preferences for each site in WSN/1933 and Perth/2009 are also shown.
}
\end{figure*}

@@

\begin{suppfigure}
\centerline{\includegraphics[width=0.6\textwidth]{figs/S02_SangerSeq/SangerSeq.pdf}}
\caption{\label{suppfig:SangerSeq}
{\bf Sanger sequencing of 30 clones from the mutant plasmid libraries.} 
(A) 
(B)
(C)
(D)
(E)
}
\end{suppfigure}
